Countering language attrition with PanLex and the Web of Data

### 2013-01-02 paper/2012/SWJ-PanLex/paper.tex
Hm, possible conflict

The lexical database of the PanLex project is based on different sources like monolingual dictionaries,
bilingual dictionaries, multilingual dictionaries, glossaries, standards, and thesauri.
The list of used sources can also be found on the web\footnote{\url{http://panlex.org/tech/plrefs.shtml}}.

@@

%As in the original PanLex database there are also \emph{expressions} used in the RDF dataset.
\begin{itemize}
\item Expressions are modeled as intances of \vocab{plx:Expression}.
Their textual representations and normalized versions thereof become the 
values of the properties \texttt{\small rdfs:label} and \texttt{\small plx:degradedText}, respectively.
Their corresponding language variety is stated
using \texttt{\small plx:languageVariety}.

>>>>

The lexical database of the PanLex project is based on different sources like monolingual dictionaries,
bilingual dictionaries, multilingual dictionaries, glossaries, standards, and thesauri.
The list of used sources can also be found on the Web\footnote{\url{http://panlex.org/tech/plrefs.shtml}}.

@@

%As in the original PanLex database there are also \emph{expressions} used in the RDF dataset.
\begin{itemize}
\item Expressions are modeled as intances of the class \texttt{\small plx:Expression}.
Their original and normalized textual representations become the 
values of the properties \texttt{\small rdfs:label} and \texttt{\small plx:degradedText}, respectively.
Their corresponding language variety is stated
using \texttt{\small plx:languageVariety}.
